Yelp Academic Dataset Final Report

### 2016-08-09 paper/paper.Rmd
abstract

---
title: "Final Paper"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(magrittr)
library(ggmap)
library(tidytext)
library(maps)
library(extrafont)
library(wordcloud)
library(stringr)
library(purrr)
source("../functions/WordCloud.R")
source("../functions/PercentAccuracy.R")
source("../functions/MeanStar.R")
font_import()
loadfonts()
```

@@

Instead, we ended up with a bar graph, which clearly shows which state has the most number of businesses with over 300 reviews. There were 6 distinct regions in total. Interestingly, the graph shows that the majority of the businesses is located in two states: about 62% of the filtered businesses were located in Nevada and another 31% was in Arizona. 
```{r business, echo = FALSE, fig.align = "center",message = FALSE, fig.height = 3.5}
ggplot(ratings_business,aes(x=stars, y=count)) +  
  geom_point(col = rgb(0,0,1,0.25), pch = 16, cex = 2) +
  scale_y_continuous(limits=c(300,5000)) +
  xlab("Star Ratings") + 
  ylab("Review Counts") +
  theme(text = element_text(family = "Times New Roman"))

ggplot(successful_business, aes(x = reorder(state, -num), 
                                y= num)) + 
  geom_bar(stat = "identity", 
           position = "dodge") +
  xlab("State") + 
  ylab("Number of Businesses") +
  theme(text = element_text(family = "Times New Roman"))
```

@@

####B. Sentiment Analysis
We hypothesized that words with higher valence scores would produce higher Yelp star ratings for businesses. First, using the R library “wordcloud”, we formed two word clouds for the 100 most frequent words in text reviews with one-star and five-star ratings to determine if there was a distinct difference between the words used.

@@

ggplot(avg_star_reviews, aes(x = avg_star, 
                             fill = most_reviewed)) + 
  geom_density(alpha = 0.5,
               color = NA) +
  labs(title = "Reviewers' Behavior Changes When In Unfamilar Locations") +
  xlab("Average Star Ratings") + 
  ylab("Density") +
  scale_fill_manual(name ="Regions",
                    values = c("blue", "red"),
                    labels = c("Familiar", "Unfamiliar"))
```
\begin{center}
\textbf{Figure 8: "Reviewers' Behavior Changes When In Unfamilar Locations"}
\end{center}

@@

##Conclusion
In conclusion, we investigated several questions related to the Yelp datasets, and our results were promising.

>>>>

---
title: "Yelp Academic Dataset Final Report"
author: Anuj Desai & Irene Lee
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(magrittr)
library(tidytext)
library(maps)
library(extrafont)
library(wordcloud)
library(stringr)
library(purrr)
source("../functions/WordCloud.R")
source("../functions/PercentAccuracy.R")
source("../functions/MeanStar.R")
font_import()
loadfonts()
```

## Abstract

This paper explores the deep dataset of Round 7 of the Yelp Academic Dataset challenge. With three primary foci, we wanted to analyze the relationship between business attributes and rating, to use sentiment analysis tools to determine the correlation between text in Yelp reviews and the business's rating, and finally to analyze user behavior in unfamiliar locations when reviewers travel. Our findings revealed that while there was no significant evidence of any relationship between business attributes and rating and travel and user rating, there was strong evidence that suggested that review text could predict star rating.

@@

Instead, we ended up with a bar graph, which clearly shows which state has the most number of businesses with over 300 reviews. There were 6 distinct regions in total. Interestingly, the graph shows that the majority of the businesses is located in two states: about 62% of the filtered businesses were located in Nevada and another 31% was in Arizona. 
```{r business, echo = F, fig.align = "center", message = F, fig.height = 3.5}
ggplot(ratings_business, aes(x = stars, y = count)) +  
  geom_point(col = rgb(0, 0, 1, 0.25), pch = 16, cex = 2) +
  scale_y_continuous(limits = c(300, 5000)) +
  xlab("Star Ratings") + 
  ylab("Review Counts") +
  theme(text = element_text(family = "Times New Roman"))

ggplot(successful_business, aes(x = reorder(state, -num), 
                                y = num)) + 
  geom_bar(stat = "identity", 
           position = "dodge") +
  xlab("State") + 
  ylab("Number of Businesses") +
  theme(text = element_text(family = "Times New Roman"))
```

@@

####B. Sentiment Analysis
We hypothesized that words with higher valence scores would produce higher Yelp star ratings for businesses. First, using the R library “__wordcloud__”, we formed two word clouds for the 100 most frequent words in text reviews with one-star and five-star ratings to determine if there was a distinct difference between the words used.

@@

ggplot(avg_star_reviews, aes(x = avg_star, 
                             fill = most_reviewed)) + 
  geom_density(alpha = 0.5,
               color = NA) +
  xlab("Average Star Ratings") + 
  ylab("Density") +
  scale_fill_manual(name ="Regions",
                    values = c("blue", "red"),
                    labels = c("Familiar", "Unfamiliar")) +
  theme(text = element_text(family = "Times New Roman"))
```
\begin{center}
\textbf{Figure 8: "Reviewers' Behavior Changes When In Unfamilar Locations"}
\end{center}

@@

##Conclusion
In conclusion, we investigated several questions related to the Yelp academic dataset, and our results were promising.
